The extended light profiles of the Sculptor and Ursa Minor dwarf galaxies: Tides or nature?

### 2025-09-09 thesis/introduction.tex
thesis updates

Simulating dwarf galaxies accurately in a cosmological context remains a
challenge. Cosmological simulations can predict the overall abundance of
the most massive dwarf galaxies \citep[e.g.,][]{sawala+2016} and broadly
examine the effects of tides \citep[e.g.,][]{riley+2024}. However,
simulated dwarf galaxies are often near the resolution limit.
Insufficient resolution can lead to artificial disruption of dwarf
galaxies and over-prediction of tidal effects
\citep[e.g.,][]{vandenbosch+2018, santos-santos+2025}. To address this
challenge, idealized simulations are often used to simulate a single
subhalo in an approximate host potential, achieving excellent numerical
convergence. For instance, the simulations we describe later reach 3
times higher resolution than Aquarius \citep{springel+2008} at a
fraction of the computational cost (400 times fewer particles).
Idealized simulations make numerous simplifications, neglecting mergers,
cosmological context, mass assembly, and often baryonic physics. We
shall use idealized simulations here to assess tidal effects after
infall.

@@

\citet{hayashi+2003}

\citet{klimentowski+2009} shows that tides can cause a disky dwarf
galaxy to transition into a spheroidal galaxy, and the velocity
dispersion and maximum circular velocity are reasonable tracers of total
mass.

@@

\citet{green+vandenbosch2019}

@@

>>>>

Simulating dwarf galaxies accurately in a cosmological context remains a
challenge. Cosmological simulations can predict the overall abundance of
the most massive dwarf galaxies \citep[e.g.,][]{sawala+2016} and broadly
examine the effects of tides \citep[e.g.,][]{riley+2024}. However,
simulated dwarf galaxies are often near the resolution limit.
Insufficient resolution can lead to artificial disruption of dwarf
galaxies and over-prediction of tidal effects
\citep[e.g.,][]{vandenbosch+2018, santos-santos+2025}. To address this
challenge, idealized simulations are often used to simulate a single
subhalo in an approximate host potential, achieving excellent numerical
convergence. For instance, the simulations we describe later reach 3
times higher resolution than Aquarius \citep{springel+2008} at a
fraction of the computational cost (400 times fewer particles).
Idealized simulations make numerous simplifications, neglecting mergers,
cosmological context, mass assembly, and often baryonic physics {[}e.g.,
\citet{hayashi+2003}; bullock+johnston2005; \citet{klimentowski+2009};
\citet{ogiya+2019}{]}. We shall use idealized simulations here to assess
tidal effects after infall.

@@

@@

\citet{hayashi+2003}, \citet{green+vandenbosch2019}

@@

\textbf{todo: finish this synthesis}
